Query Optimization for Dynamic Imputation

### 2017-05-05 paper/examples.tex

\begin{figure}
  \Tree
  [.$\pi_{\text{income, AVG(white\_blood\_cell\_ct)}}$
    [.$g_{\text{income, AVG(white\_blood\_cell\_ct)}}$
      [.\colorbox{pink}{$\mu_{\text{demo.income}}$}
        [.$\bowtie_{\text{exams.id} = \text{demo.id}}$
          [.\colorbox{pink}{$\mu_{\text{labs.white\_blood\_cell\_ct}}$}
            [.$\bowtie_{\text{exams.id} = \text{labs.id}}$
              [.$\sigma_{\text{exams.weight} \geq 120}$ 
                [.\colorbox{pink}{$\mu_{\text{exams.weight}}$} exams ] 
              ] 
              labs 
            ]
          ]
        [.$\sigma_{\text{demo.gender} = 2}$ demo ]
      ] 
    ] 
  ] 
  ]
\vspace{0.5\baselineskip}
\caption{A quality-optimized plan for the query in~\Cref{fig:example-query}. The operators $\sigma$, $\pi$, $\bowtie$, and $g$ are the standard relational selection, projection, join, and group-by/aggregate, $\mu$ and $\delta$ are specialized imputation operators (\Cref{sec:operators}).}
\label{fig:quality-plan}
\end{figure}

@@

\begin{figure}
\Tree
  [.$\pi_{\text{income, AVG(white\_blood\_cell\_ct)}}$
    [.$g_{\text{income, AVG(white\_blood\_cell\_ct)}}$
      [.\colorbox{pink}{$\delta_{\text{demo.income, labs.white\_blood\_cell\_ct}}$}
        [.$\bowtie_{\text{exams.id} = \text{labs.id}}$
          [.$\bowtie_{\text{demo.id} = \text{exams.id}}$
            [.$\sigma_{\text{demo.gender} = 2}$ demo ]
            [.$\sigma_{\text{exams.weight} \geq 120}$ [.\colorbox{pink}{$\delta_{\text{exams.weight}}$} exams ] ] ] labs ] ] ] ]
\caption{A performance-optimized plan for the query in~\Cref{fig:example-query}.The operators $\sigma$, $\pi$, $\bowtie$, and $g$ are the standard relational selection, projection, join, and group-by/aggregate, $\mu$ and $\delta$ are specialized imputation operators (\Cref{sec:operators}).}
\label{fig:fast-plan}
\end{figure}

>>>>

\begin{figure}
  \begin{subfigure}{\columnwidth}
    \Tree
  [.$\pi_{\text{income, AVG(white\_blood\_cell\_ct)}}$
    [.$g_{\text{income, AVG(white\_blood\_cell\_ct)}}$
      [.\colorbox{pink}{$\mu_{\text{demo.income}}$}
        [.$\bowtie_{\text{exams.id} = \text{demo.id}}$
          [.\colorbox{pink}{$\mu_{\text{labs.white\_blood\_cell\_ct}}$}
            [.$\bowtie_{\text{exams.id} = \text{labs.id}}$
              [.$\sigma_{\text{exams.weight} \geq 120}$ 
                [.\colorbox{pink}{$\mu_{\text{exams.weight}}$} exams ] 
              ] 
              labs 
            ]
          ]
        [.$\sigma_{\text{demo.gender} = 2}$ demo ]
      ] 
    ] 
  ] 
  ]
  \caption{A quality-optimized plan for the query in~\Cref{fig:example-query}.}
\label{fig:quality-plan}
\end{subfigure}
  \begin{subfigure}{\columnwidth}
\vspace{1em}
\Tree
  [.$\pi_{\text{income, AVG(white\_blood\_cell\_ct)}}$
    [.$g_{\text{income, AVG(white\_blood\_cell\_ct)}}$
      [.\colorbox{pink}{$\delta_{\text{demo.income, labs.white\_blood\_cell\_ct}}$}
        [.$\bowtie_{\text{exams.id} = \text{labs.id}}$
          [.$\bowtie_{\text{demo.id} = \text{exams.id}}$
            [.$\sigma_{\text{demo.gender} = 2}$ demo ]
            [.$\sigma_{\text{exams.weight} \geq 120}$ [.\colorbox{pink}{$\delta_{\text{exams.weight}}$} exams ] ] ] labs ] ] ] ]
\caption{A performance-optimized plan for the query in~\Cref{fig:example-query}.}
\label{fig:fast-plan}
\end{subfigure}
\vspace{1em}

\caption{The operators $\sigma$, $\pi$, $\bowtie$, and $g$ are the standard relational selection, projection, join, and group-by/aggregate, $\mu$ and $\delta$ are specialized imputation operators (\Cref{sec:operators}). The imputation operators are highlighted.}
\end{figure}

@@
